---
title: "Final Project"
author: "Andrew Parsons"
date: "September 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(Quandl)
```
##### Big thing is that you will need to change the api key to yours whenever you are writing 

#Developed Market

### US 
###Index
Quandl("NASDAQOMX/NQUSB", api_key="ZD8hU_zfyaksm86ayy2B")
### Large Cap
Quandl("NASDAQOMX/NQUSL", api_key="ZD8hU_zfyaksm86ayy2B")
### Mid Cap
Quandl("NASDAQOMX/NQUSM", api_key="ZD8hU_zfyaksm86ayy2B")
### Small Cap
Quandl("NASDAQOMX/NQUSS", api_key="ZD8hU_zfyaksm86ayy2B")


### UK Index
Quandl("NASDAQOMX/NQGB", api_key="ZD8hU_zfyaksm86ayy2B")
### UK Large Cap 
Quandl("NASDAQOMX/NQGBLC", api_key="ZD8hU_zfyaksm86ayy2B") 
### UK Mid cap 
Quandl("NASDAQOMX/NQGBMC", api_key="ZD8hU_zfyaksm86ayy2B") 
### UK Small cap 
Quandl("NASDAQOMX/NQGBSC", api_key="ZD8hU_zfyaksm86ayy2B")

### Hong Kong 
### Index
Quandl("NASDAQOMX/NQHKHKD", api_key="ZD8hU_zfyaksm86ayy2B")
### Large Cap
Quandl("NASDAQOMX/NQHKLCHKD", api_key="ZD8hU_zfyaksm86ayy2B")
### Mid Cap
Quandl("NASDAQOMX/NQHKMCHKD", api_key="ZD8hU_zfyaksm86ayy2B")
### Small Cap
Quandl("NASDAQOMX/NQHKSCHKD", api_key="ZD8hU_zfyaksm86ayy2B")


### Israel 
### Index
Quandl("NASDAQOMX/NQIL", api_key="ZD8hU_zfyaksm86ayy2B")
### Large Cap
Quandl("NASDAQOMX/NQILLM", api_key="ZD8hU_zfyaksm86ayy2B") 
### Mid Cap
Quandl("NASDAQOMX/NQILMC", api_key="ZD8hU_zfyaksm86ayy2B") 
### Small Cap
Quandl("NASDAQOMX/NQILSC", api_key="ZD8hU_zfyaksm86ayy2B")


#Emerging Market

### Mexico 
### Index
Quandl("NASDAQOMX/NQMX", api_key="ZD8hU_zfyaksm86ayy2B")
### Large Cap
Quandl("NASDAQOMX/NQMXLC", api_key="ZD8hU_zfyaksm86ayy2B")
### Mid Cap
Quandl("NASDAQOMX/NQMXMC", api_key="ZD8hU_zfyaksm86ayy2B")
### Small Cap
Quandl("NASDAQOMX/NQMXSC", api_key="ZD8hU_zfyaksm86ayy2B")


### Russian 
### Index
Quandl("NASDAQOMX/NQRU", api_key="ZD8hU_zfyaksm86ayy2B")
### Large Cap
Quandl("NASDAQOMX/NQRULC", api_key="ZD8hU_zfyaksm86ayy2B)
### Mid Cap
Quandl("NASDAQOMX/NQRUMC", api_key="ZD8hU_zfyaksm86ayy2B")
### Small Cap
Quandl("NASDAQOMX/NQRUSC", api_key="ZD8hU_zfyaksm86ayy2B"

### China 
### Index
Quandl("NASDAQOMX/NQCNCNY", api_key="ZD8hU_zfyaksm86ayy2B")
### Large Cap
Quandl("NASDAQOMX/NQCNLCCNY", api_key="ZD8hU_zfyaksm86ayy2B")
### Mid Cap
Quandl("NASDAQOMX/NQCNMCCNY", api_key="ZD8hU_zfyaksm86ayy2B")
### Small Cap
Quandl("NASDAQOMX/NQCNSCCNY", api_key="ZD8hU_zfyaksm86ayy2B")


### Egypt 
### Index
Quandl("NASDAQOMX/NQEGEGP", api_key="ZD8hU_zfyaksm86ayy2B")
### Large Cap
Quandl("NASDAQOMX/NQEGLMEGP", api_key="ZD8hU_zfyaksm86ayy2B") 
### Mid cap
Quandl("NASDAQOMX/NQEGMCEGP", api_key="ZD8hU_zfyaksm86ayy2B")
### Small Cap
Quandl("NASDAQOMX/NQEGSCEGP", api_key="ZD8hU_zfyaksm86ayy2B"


### Gold and Precious Medals
Quandl("NASDAQOMX/QGLD", api_key="ZD8hU_zfyaksm86ayy2B")


### Oil and Gas
Quandl("NASDAQOMX/NQG0001", api_key="ZD8hU_zfyaksm86ayy2B")

### Global Agriculture 
Quandl("NASDAQOMX/QAGR", api_key="ZD8hU_zfyaksm86ayy2B")


### Examples:
### Here I was just attributing a certain amount of data to UK1
```{r}
UK1 <- Quandl("NASDAQOMX/NQGB", api_key="ZD8hU_zfyaksm86ayy2B", start_date='2017-01-01', end_date='2018-01-01')
```


### This was just to check the first two columns of NQGB
```{r}
Quandl("NASDAQOMX/NQGB", api_key="ZD8hU_zfyaksm86ayy2B", column_index = '1')
```


```{r}
ggplot(data = UK1) +
  geom_line(aes(x = as.Date(UK1$`Trade Date`), 
                y = as.numeric(UK1$`Index Value`)
                )
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8)
)
  
```

```{r}
RU1 <- Quandl("NASDAQOMX/NQRU", api_key="ZD8hU_zfyaksm86ayy2B", start_date='2017-01-01', end_date='2018-01-01')
```


Russian line graph
```{r}
ggplot(data = RU1) +
  geom_line(aes(x = as.Date(RU1$`Trade Date`), 
                y = as.numeric(RU1$`Index Value`)
                )
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8))
```


### Need to create  a data fram enclosing both to actually put them both on a plot


```{r}
test_data <- data.frame(UK1,RU1
)
```


### Tested to get the first 6 trems of the new data fram set


```{r}
head(test_data)
```

### Utilizing the data frame was able to plot both lines on the same graph


```{r}
ggplot(data = test_data) +
  geom_line(aes(x = as.Date(RU1$`Trade Date`), 
                y = as.numeric(RU1$`Index Value`)
                ), 
            color = "red"
            ) +
  geom_line(aes(x = as.Date(UK1$`Trade Date`), 
                y = as.numeric(UK1$`Index Value`)
                ),
            color = "blue"
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30))
```


Hong Kong
```{r}
# index
HKindex <- Quandl("NASDAQOMX/NQHKHKD", api_key="ZD8hU_zfyaksm86ayy2B", start_date='2017-01-01', end_date='2018-01-01')

### Large Cap
HKlarge <- Quandl("NASDAQOMX/NQHKLCHKD", api_key="ZD8hU_zfyaksm86ayy2B", start_date='2017-01-01', end_date='2018-01-01')

### Mid Cap
HKmid <- Quandl("NASDAQOMX/NQHKMCHKD", api_key="ZD8hU_zfyaksm86ayy2B", start_date='2017-01-01', end_date='2018-01-01')

### Small Cap
HKsmall <- Quandl("NASDAQOMX/NQHKSCHKD", api_key="ZD8hU_zfyaksm86ayy2B", start_date='2017-01-01', end_date='2018-01-01')
```


Hong Kong Index
```{r}
ggplot(data = HKindex) +
  geom_line(aes(x = as.Date(HKindex$`Trade Date`), 
                y = as.numeric(HKindex$`Index Value`)
                )
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8)
)
```

Hong Kong Large
```{r}
ggplot(data = HKlarge) +
  geom_line(aes(x = as.Date(HKlarge$`Trade Date`), 
                y = as.numeric(HKlarge$`Index Value`)
                )
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8)
)
```

Hong Kong Mid
```{r}
ggplot(data = HKmid) +
  geom_line(aes(x = as.Date(HKmid$`Trade Date`), 
                y = as.numeric(HKmid$`Index Value`)
                )
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8)
)
```

Hong Kong Small
```{r}
ggplot(data = HKsmall) +
  geom_line(aes(x = as.Date(HKsmall$`Trade Date`), 
                y = as.numeric(HKsmall$`Index Value`)
                )
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8)
)
```

Combined Hong Kong Data Frame
```{r}
HK_index_caps <- data.frame(HKindex, HKlarge, HKmid, HKsmall)
```

Combined Hong Kong Graphs
```{r}
ggplot(data = HK_index_caps) +
  geom_line(aes(x = as.Date(HKindex$`Trade Date`), 
                y = as.numeric(HKindex$`Index Value`)
                ), 
            color = "black"
            ) +
  geom_line(aes(x = as.Date(HKlarge$`Trade Date`), 
                y = as.numeric(HKlarge$`Index Value`)
                ),
            color = "blue"
            ) +
  geom_line(aes(x = as.Date(HKmid$`Trade Date`), 
                y = as.numeric(HKmid$`Index Value`)
                ),
            color = "green"
            ) +
  geom_line(aes(x = as.Date(HKsmall$`Trade Date`), 
                y = as.numeric(HKsmall$`Index Value`)
                ),
            color = "red"
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30))
```









China
```{r}
### Index
CHindex <- Quandl("NASDAQOMX/NQCNCNY", api_key="ZD8hU_zfyaksm86ayy2B", start_date='2017-01-01', end_date='2018-01-01')

### Large Cap
CHlarge <- Quandl("NASDAQOMX/NQCNLCCNY", api_key="ZD8hU_zfyaksm86ayy2B", start_date='2017-01-01', end_date='2018-01-01')

### Mid Cap
CHmid <- Quandl("NASDAQOMX/NQCNMCCNY", api_key="ZD8hU_zfyaksm86ayy2B", start_date='2017-01-01', end_date='2018-01-01')

### Small Cap
CHsmall <- Quandl("NASDAQOMX/NQCNSCCNY", api_key="ZD8hU_zfyaksm86ayy2B", start_date='2017-01-01', end_date='2018-01-01')
```

China Index
```{r}
ggplot(data = CHindex) +
  geom_line(aes(x = as.Date(CHindex$`Trade Date`), 
                y = as.numeric(CHindex$`Index Value`)
                )
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8)
)
```

China Large Cap
```{r}
ggplot(data = CHlarge) +
  geom_line(aes(x = as.Date(CHlarge$`Trade Date`), 
                y = as.numeric(CHlarge$`Index Value`)
                )
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8)
)
```

China Mid Cap
```{r}
ggplot(data = CHmid) +
  geom_line(aes(x = as.Date(CHmid$`Trade Date`), 
                y = as.numeric(CHmid$`Index Value`)
                )
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8)
)
```

China Small Cap
```{r}
ggplot(data = CHsmall) +
  geom_line(aes(x = as.Date(CHsmall$`Trade Date`), 
                y = as.numeric(CHsmall$`Index Value`)
                )
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30, hjust = 0.8)
)
```

China Combined Data Frame
```{r}
CH_index_caps <- data.frame(CHindex, CHlarge, CHmid, CHsmall)
```

China Combined Graphs
```{r}
ggplot(data = CH_index_caps) +
  geom_line(aes(x = as.Date(CHindex$`Trade Date`), 
                y = as.numeric(CHindex$`Index Value`)
                ), 
            color = "black"
            ) +
  geom_line(aes(x = as.Date(CHlarge$`Trade Date`), 
                y = as.numeric(CHlarge$`Index Value`)
                ),
            color = "blue"
            ) +
  geom_line(aes(x = as.Date(CHmid$`Trade Date`), 
                y = as.numeric(CHmid$`Index Value`)
                ),
            color = "green"
            ) +
  geom_line(aes(x = as.Date(CHsmall$`Trade Date`), 
                y = as.numeric(CHsmall$`Index Value`)
                ),
            color = "red"
            ) +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "Months",
       y = "Index Value") +
  theme(axis.text.x = element_text(angle = 30))
```








